### 2010-12-23 paper.tex
Edited paper to reflect Seth's comments

\frenchspacing \title{Out-of-Sample Comparisons of Overfit Models}
\author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I
    would like to thank Julian Betts, Marjorie Flavin, Nir Jaimovich,
    Lutz Kilian, Michael McCracken, Seth Pruitt, Ross Starr, Yixiao
    Sun, Allan Timmermann, participants at the 2010 Midwest Economics
    Association Annual Meetings, the 2010 Joint Statistical Meetings,
    and in many seminars at \textsc{ucsd}, and espeically Graham
    Elliott for their valuable suggestions, feedback and advice in
    writing this paper.  I would also like to thank Amit Goyal for
    providing computer code and data for his 2008 RFS paper with Ivo
    Welch \citep{goyal-welch-2008-rfs}.} \\ Iowa State University,
  Economics Department}

@@

\begin{abstract}\thispagestyle{empty}\noindent
  This paper uses dimension asymptotics to study why overfit linear
  regression models should be compared out-of-sample; we let the number of
  predictors used by the larger model increase with the number of
  observations so that their ratio remains uniformly positive.  Under
  this limit theory, the naive Diebold-Mariano-West out-of-sample test
  can test hypotheses about a key quantity for evaluating forecasting
  models---a time series analogue to the generalization error---as
  long as the out-of-sample period is small relative to the total
  sample size.  Moreover, tests that are designed to reject if the
  larger model is true, such as the usual in-sample Wald and
  \textsc{lm} tests and also Clark and McCracken's (2001, 2005a),
  \citepos{mccracken_asymptotics_2007} and Clark and West's (2006,
  2007) out-of-sample statistics, will choose the larger model too
  often when the smaller model is more accurate.

@@

Although \oos\ comparisons have been popular in macroeconomics and
finance since \citepos{meese_empirical_1983} seminal study of exchange
rate models, it is unclear from a theoretical perspective whether or
not the statistics are useful.  Empirical researchers often cite
``overfit'' or ``instability'' as reasons for using \oos\ comparisons,
as in \citet{stock_forecasting_2003}, but neither term is precisely
defined or formalized.  Compounding this problem, the asymptotic
distributions of these statistics are derived under conditions that
rule out either instability or overfit and allow a researcher to use a
conventional in-sample comparison---a variation of the F-test, for
example.  As \citet{inoue_kilian_2004} argue, the statistics
themselves are designed to test hypotheses that can be tested by these
in-sample statistics.  For example, \citet{diebold_comparing_1995} and
\citet{west_asymptotic_1996} derive the limiting distributions of many
popular \oos\ test statistics under conditions that would justify
these full-sample tests.\footnote{In this paper, we will refer to
  their basic \oos\ $t$-test as the \dmw\ test.}  Much of the
subsequent research by \citet{chao_out_2001},
\citet{clark_tests_2001,clark_evaluating_2005},
\citet{corradi_consistent_2002,corradi_recent_2004},
\citet{clark_using_2006,clark_approximately_2007},
\citet{mccracken_asymptotics_2007}, \citet{anatolyev_inference_2008},
and others relaxes several of Diebold and Mariano's and West's
assumptions, but maintains the stationarity and dependence conditions
that permit in-sample comparisons.\footnote{Like us,
  \citet{anatolyev_inference_2008} allows the number of regressors to
  increase with $T$.  But in that paper, they increase slowly enough
  that the \ols\ coefficients are consistent and asymptotically
  normal.}  \citet{giacomini_tests_2006}, and
\citet{giacomini-rossi-2009-REStud,giacomini-rossi-2010-JAppliedEconometrics}
are exceptions.  Instead of focusing on hypotheses that can be tested
by in-sample comparisons, \citet{giacomini_tests_2006} derive an \oos\
test for the null hypothesis that the difference between two models'
\oos\ forecasting performance is unpredictable, a martingale
difference sequence, \citet{giacomini-rossi-2009-REStud} test whether
the \oos\ forecasting performance of a model suffers from a breakdown
relative to its in-sample performance, and
\citet{giacomini-rossi-2010-JAppliedEconometrics} test whether the
forecasting performance is stable. However, those papers focus on a
particular \oos\ estimation strategy and do not address why naive
\oos\ comparisons might be generally useful.

Since in-sample and \oos\ statistics require similar assumptions and
test similar hypotheses, one might expect that they would give similar
results.  They do not.  Generally in-sample analysis supports more
complicated theoretical models and \oos\ analysis supports simple
benchmarks, as seen in \citet{meese_empirical_1983},
\citet{stock_forecasting_2003}, and \citet{goyal-welch-2008-rfs}.
Since these different approaches strongly influence the outcome of
research, it is important to know when each is appropriate.  The
explanations in favor of \oos\ comparisons claim that they should be
more robust to unmodeled instability
\citep{clark_power_2005,giacomini_tests_2006,giacomini-rossi-2009-REStud,giacomini-rossi-2010-JAppliedEconometrics}
or to overfit \citep{mccracken_data_1998,clark_can_2004}.  Both
explanations presume that the in-sample comparison is invalid and the
\oos\ comparisons are more reliable.  Of course, as
\citet{inoue_kilian_2004,inoue_selection_2006} point out, both
in-sample and \oos\ methods could be valid, but the \oos\ methods
could have lower power.

In this paper, we study the ``overfit'' possibility and leave
``instability'' to future research. This paper uses dimension
asymptotics to study the behavior of \oos\ comparisons when at least
one of the models is overfit---when the number of its regressors
increases with the number of observations so that their ratio remains
positive.  We focus on linear regression models estimated with a fixed
training window, but our basic conclusions should be true for other
estimation strategies and models as well.  We show that the usual
\oos\ average is asymptotically normal and can consistently estimate
the difference between the models' expected loss in periods
$T+1,T+2,\dots$ conditional on the on the data available in period
$T$, a time-series analogue to the generalization error.\footnote{See,
  for example, \citet{elemstatlearning}.}  Under these asymptotics,
the generalization error does not converge to the expected performance
of the pseudo-true models, so the in-sample and \oos\
comparisons measure different quantities and should be expected to
give different results for reasons beyond simple size and power
comparisons.  Under our theory, the model that is closer to the true
\dgp\ in population can forecast worse.  In such a situation, an
in-sample comparison would correctly reject the null hypothesis that
the benchmark is true, and an \oos\ comparison would correctly fail to
reject the null that the benchmark is more accurate.\footnote{In a
  pair of papers similar to ours,
  \citet{RePEc:fip:fedkrw:rwp09-10,RePEc:fip:fedkrw:rwp09-11} study
  in-sample and \oos\ tests that the larger model has nonzero
  coefficients that are too close to zero to expect the model to
  forecast more accurately.  Like this paper, they argue that the
  larger model can be true but less accurate.  However, they focus on
  an aspect of the \dgp\ that makes this phenomenon likely, while we
  focus on the coefficient estimates that produce less accurate
  forecasts.}

This result justifies \oos\ comparisons when researchers want to
choose a model for forecasting.  Although there has been little
emphasis on hypothesis testing in these settings, testing is usually
appropriate: there is usually a familiar benchmark model in place, and
the cost of incorrectly abandoning the benchmark for a less accurate
alternative model is higher than the cost of incorrectly failing to
switch to a more accurate alternative.\footnote{These costs can be
  monetary, in the form of computer upgrades, software installation,
  and training, or they can be reputational costs.}
We show that the \dmw\ test lets the forecaster control the
probability of the first error, just as with conventional hypothesis
testing.

However, since the models' coefficients are imprecisely
estimated, the test sample must be small to ensure that the model
estimated over the training sample is similar to the one that will be
estimated over the full sample.  In particular, $P/T \to 0$ is
required for consistent estimation, and $P^2/T \to 0$ is required for
valid confidence intervals and inference.  For larger $P$, the \oos\
comparisons remain asymptotically normal, but are centered on the
forecasting performance associated with the period-$R$ estimates.  In
practice, researchers typically use large values of $P$, so these
studies may be too pessimistic about their models' future accuracy if
they use the \dmw\ test.  Section~\ref{sec:oostheory} lays out the
asymptotic behavior of the \dmw\ test under this limit theory.

Under this asymptotic theory, the \ols\ coefficient estimator is no
longer consistent or asymptotically normal \citep{huber_robust_1973},
so this is a useful way to model overfit and imprecisely estimated
models.  Moreover, \citet{efron_biased_1986,efron_estimation_2004}
shows that in-sample comparisons overestimate models' accuracy by a
factor proportional to this ratio.  Despite the non-normality of the
coefficient estimators, modifications of the F-test are valid under
this asymptotic theory, as shown by \citet{boos_anova_1995},
\citet{akritas_asymptotics_2000},
\citet{akritas_heteroscedastic_2004}, and
\citet{calhoun_hypothesis_2009}, among others.  The F-test and Wald
tests are no longer asymptotically valid themselves.  Such results
establish that hypotheses about the parameters of the \dgp\ can be
tested in-sample even if one or both models are overfit.  For that
very reason, these tests can not reliably choose a model for
forecasting and will reject the benchmark too often.  We show this
analytically in Section~\ref{sec:insample}.  Moreover, under this
asymptotic theory, many recent \oos\ test statistics, such as those
derived by \cite{clark_tests_2001,clark_evaluating_2005},
\citet{mccracken_asymptotics_2007}, and
\citet{clark_using_2006,clark_approximately_2007} should behave like
the F-test.  These tests are also designed to reject the benchmark
when the alternative model is true, and so they may reject too often
when the benchmark is false but more accurate.  Obviously, since the
distribution of these statistics converges to the normal when $P/T \to
\infty$ (with the number of regressors fixed), these statistics behave
like the \dmw\ test when $P$ is small, but should over-reject the
benchmark when $P$ is large.  Section~\ref{sec:mc} presents
simulations that support these claims.

@@

The rest of the paper proceeds as follows.
Section~\ref{sec:assumptions} introduces our notation and assumptions.
Section~\ref{sec:theory} gives the main theoretical results for the
\dmw\ \oos\ test and shows that the F-test rejects the benchmark model
too often when it is false but more accurate than the
alternative. Section~\ref{sec:mc} presents a Monte Carlo study
supporting our theoretical results.  Section~\ref{sec:empirics}
applies the \oos\ statistic to \citepos{goyal-welch-2008-rfs} dataset
for equity premium prediction, and Section~\ref{sec:conclusion}
concludes.  Proofs and supporting results are listed in the Appendix.

@@

The first assumption is a standard condition on the dependence of the
underlying stochastic array.  We assume that the array is absolutely
regular instead of strong mixing, which is more common in
econometrics, because absolute regularity admits a particular coupling
argument \citep{berbee_random_1979} that is unavailable for strong
mixing sequences.

Assumption \ref{asmp-2} rules out uninteresting cases where the
forecast error vanishes.
\begin{asmp}\label{asmp-2}
  The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
  positive and finite, and all of the eigenvalues of the covariance
  matrix of $x_t$ are uniformly positive and finite as well.  The
  Euclidean norms of the pseudo-true coefficients, $\theta_1$ and
  $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and $|\theta_2|_2 = O(1)$.
  Moreover, there exist a $\delta > 0$ and finite $\Delta$ such that
  \begin{equation*}
    \lVert \lambda_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{4+\delta}
    \leq S_{T}\, \Delta \\
    \lVert
    \lambda_{\max}(X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})
    \rVert_{4+\delta} \leq S_{T}\, \Delta \\
    \lVert \lambda_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1}) \rVert_{4+\delta} \leq \Delta/S_{T} \\
    \lVert
    \lambda_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{4+\delta}
    \leq \Delta/S_{T}
  \end{equation*}
  for all $S_{T} \geq K_{2T}$ and large enough $T$, with $i =
  1,2$,
  \[ X_{iT} \equiv [x_{i1} \quad \dots \quad x_{i,T-\h}]' \]
  and
  \[ \ep{iT} = (\varepsilon_{i,1+\h}, \dots, \varepsilon_{i,T})'.\]
\end{asmp}

@@

This third assumption establishes basic moment and smoothness
conditions for the \oos\ loss.  The differentiability
condition is weak and allows the loss function itself to be
nondifferentiable; for example, absolute error and many asymmetric loss functions
satisfy this assumption.

@@

The requirements that $P$ and $R$ grow with $T$ are common.  Parts of
the assumption are new, in particular the requirement that $P^2/T \to
0$.  See Lemma \ref{res-convergence} for a discussion of its
implications.  In practical terms, this assumption requires that the
test sample be large, that the forecaster plans to use the model for
many periods in the future, and that there is enough data that
including or excluding the test sample does not affect the estimates
of $\theta_1$ or $\theta_2$ very much.

The next assumption restricts the class of variance estimators we will
consider.  We use the same class of estimators studied by
\citet{de_jong_consistency_2000} (their class $\mathcal{K}$); see
their paper for further discussion.

@@

\begin{thm}\label{res-confidence-intervals}
  Suppose that Assumptions \ref{asmp-1}--\ref{asmp-4} hold, that
  $\hat\sigma$ is an estimator satisfying
  \[
    \hat\sigma^2 = \sigma^2 + o_p(1), \quad \text{with}\quad 
    \sigma^2 \equiv \var_R(\sqrt{P} \bar D_1),
  \]
  and that $\sigma^2$ is uniformly a.s. positive.  Then
  \[
  \frac{\bar{D}_1 - \E_T\bar{D}_2}{\hat\sigma / \sqrt{P}}
  \to^d N(0,1).
  \]
  Consequently, each of the usual Gaussian confidence intervals,
  \begin{eqnarray}
  &&[\bar{D}_1 - z_{\alpha/2} \, \hat\sigma /
      \sqrt{P}, \bar{D}_1 + z_{\alpha/2} \hat\sigma / \sqrt{P}],\label{interval-twosided} \\
  &&[\bar{D}_1 - z_{\alpha} \, \hat\sigma / \sqrt{P}, +\infty), \label{interval-greater}
  \end{eqnarray}
  and
  \begin{equation} (-\infty, \bar{D}_1 + z_{\alpha}
      \, \hat\sigma / \sqrt{P}],
  \end{equation}
  contains $\E_T\bar{D}_2$ with probability $\alpha$ in the limit,
  with $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
  distribution.
\end{thm}
The requirement that $\sigma^2$ be uniformly a.s. positive is
not restrictive under our asymptotic theory.  Since the models'
coefficients are estimated with uncertainty in the limit, the two
models give different forecasts even if they both nest the \dgp.  This
is similar to \citepos{giacomini_tests_2006} rolling-window result,
but comes from different asymptotics.

@@

Mixingales satisfies a weak-dependence condition similar to \mds es
and were introduced and studied extensively by
\citet{mcleish_dependent_1974,mcleish_invariance_1975,mcleish_maximal_1975,mcleish_invariance_1977}.
This lemma shows that the estimation uncertainty introduces dependence
into the \oos\ forecast errors, but that additional dependence is
contained in the term $\E_R \bar D_1$ and can be effectively removed
by subtraction.  The second part of the Lemma shows that the basic
mixingale \clt\ established by \citet{de_jong_central_1997} applies in
this setting.\footnote{De Jong proves two \clt s: one for mixingales
  and one for \ned\ functions of mixing processes.  His mixingale
  result makes assumptions about the behavior of the sample second
  moment that arise as consequences of \ned.  The proof of
  Lemma~\ref{res-mixingale} shows that the arguments used for de
  Jong's \ned\ \clt\ continue to hold for our \oos\ process---in
  effect, that the \oos\ process has slightly more structure than
  required for it to be a mixingale.}

@@

Finally, for Theorem \ref{res-confidence-intervals} to be useful, we
need a consistent estimator of $\sigma^2$. Lemma
\ref{res-variance-estimator} establishes that the usual \oos\ \hac\
variance estimators are consistent.\footnote{As with
      Lemma~\ref{res-mixingale}, the proof of this lemma takes
      \citepos{de_jong_consistency_2000} existing consistency results
      for \ned\ processes and shows that the same arguments can be
      applied to our \oos\ mixingale.}

@@

\section{Monte Carlo}\label{sec:mc}
\newcommand{\thetanorm}{\ensuremath{\lvert \theta \rvert_2}} This
section presents two simulations that investigate the accuracy of our
theory in small samples.\footnote{Simulations were conducted in R
  \citep{rproject} using the Lattice \citep{lattice} and RSQLite
  \citep{rsqlite} packages for graphics and data management
  respectively.}  The first looks at the asymptotic normality of the
\dmw\ statistic centered on either $E_R \bar D_1$ or $E_T \bar D_2$.
The previous section's results imply that centering on the first
should give an approximately normal statistic and centering on the
second should give a normal statistic when $P$ is small relative to
$T$.  The second simulation looks at the size and power of several
statistics when conducting inference about the difference in the
models' generalization error.

@@

Results using \citepos{mccracken_asymptotics_2007} critical values are
presented in Figure~\ref{fig:mccracken} and are similar to those using
Clark and West's test.  For $c=0$ the rejection probability is nearly
the test's nominal size.  For $c=1$, the rejection probability
increases with $P/T$, from close to the nominal size when $P/T$ is
small to over 25\% when $P/T = 2/3$.  Note that all of the simulations
use the parsimonious model.  McCracken's statistic over-rejects here
by slightly less than Clark and West's, but still by a substantial
amount.

@@

\appendix
\section{Supporting results}
The results in this paper rely heavily on a coupling argument for
absolutely regular sequences, Berbee's Lemma
\citep{berbee_random_1979}.  In fact, many of the results of this
paper (\ref{res-confidence-intervals}, \ref{res-mixingale}, and
\ref{res-variance-estimator}) are modifications of existing
results for \ned\ functions of mixing processes by
\citet{de_jong_central_1997} and \citet{de_jong_consistency_2000};
this coupling argument is used to explicitly derive inequalities that
arise naturally for \ned\ processes.  Lemma \ref{lem-basic-coupling}
establishes these inequalities, which are based on a proposition of
\citet{merlevede_coupling_2002}.

>>>>

\frenchspacing \title{Out-of-Sample Comparisons of Overfit Models}
\author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I
    would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
    Nir Jaimovich, Lutz Kilian, Michael McCracken, Seth Pruitt, Ross
    Starr, Yixiao Sun, Allan Timmermann, participants at the 2010
    Midwest Economics Association Annual Meetings, the 2010 Joint
    Statistical Meetings, and in many seminars at \textsc{ucsd}, and
    espeically Graham Elliott for their valuable suggestions, feedback
    and advice in writing this paper.  I would also like to thank Amit
    Goyal for providing computer code and data for his 2008 RFS paper
    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University,
  Economics Department}
\date{October 24, 2011}

@@

\begin{abstract}\thispagestyle{empty}\noindent
  This paper uses dimension asymptotics to study why overfit linear
  regression models should be compared out-of-sample; we let the
  number of predictors used by the larger model increase with the
  number of observations so that their ratio remains uniformly
  positive.  Under this limit theory, the naive Diebold-Mariano-West
  out-of-sample test can test hypotheses about a key quantity for
  evaluating forecasting models---a time series analogue to the
  generalization error---as long as the out-of-sample period is small
  relative to the total sample size.  Moreover, tests that are
  designed to reject if the larger model is true, such as the usual
  in-sample Wald and \textsc{lm} tests and also Clark and McCracken's
  (2001, 2005a), \citepos{Mcc:07} and Clark and West's (2006, 2007)
  out-of-sample statistics, will choose the larger model too often
  when the smaller model is more accurate.

@@

Although \oos\ comparisons have been popular in macroeconomics and
finance since \citepos{MeR:83} seminal study of exchange rate models,
it is unclear from a theoretical perspective whether or not the
statistics are useful.  Empirical researchers often cite ``overfit''
or ``instability'' as reasons for using \oos\ comparisons, as in
\citet{StW:03}, but neither term is precisely defined or formalized.
Compounding this problem, the asymptotic distributions of these
statistics are derived under conditions that rule out either
instability or overfit and allow a researcher to use a conventional
in-sample comparison---a variation of the F-test, for example.  As
\citet{InK:04} argue, the statistics themselves are designed to test
hypotheses that can be tested by these in-sample statistics.  For
example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
distributions of many popular \oos\ test statistics under conditions
that would justify these full-sample tests.\footnote{In this paper, we
  will refer to their basic \oos\ $t$-test as the \dmw\ test.}  Much
of the subsequent research by \citet{CCS:01}, \citet{ClM:01,ClM:05},
\citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07}, \citet{Mcc:07},
\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
and West's assumptions, but maintains the stationarity and dependence
conditions that permit in-sample comparisons.\footnote{Like us,
  \citet{Ana:07} allows the number of regressors to increase with $T$.
  But in that paper, they increase slowly enough that the \ols\
  coefficients are consistent and asymptotically normal.}
\citet{GiW:06}, and \citet{GiR:09, GiR:10} are exceptions.  Instead of
focusing on hypotheses that can be tested by in-sample comparisons,
\citet{GiW:06} derive an \oos\ test for the null hypothesis that the
difference between two models' \oos\ forecasting performance is
unpredictable, a martingale difference sequence, \citet{GiR:09} test
whether the \oos\ forecasting performance of a model suffers from a
breakdown relative to its in-sample performance, and \citet{GiR:10}
test whether the forecasting performance is stable. However, those
papers focus on a particular \oos\ estimation strategy and do not
address why naive \oos\ comparisons might be generally useful.

Since in-sample and \oos\ statistics require similar assumptions and
test similar hypotheses, one might expect that they would give similar
results.  They do not.  Generally in-sample analysis supports more
complicated theoretical models and \oos\ analysis supports simple
benchmarks, as seen in \citet{MeR:83}, \citet{StW:03}, and
\citet{GoW:08}.  Since these different approaches strongly influence
the outcome of research, it is important to know when each is
appropriate.  The explanations in favor of \oos\ comparisons claim
that they should be more robust to unmodeled instability
\citep{ClM:05,GiW:06,GiR:09,GiR:10} or to overfit
\citep{Mcc:98,Cla:04}.  Both explanations presume that the in-sample
comparison is invalid and the \oos\ comparisons are more reliable.  Of
course, as \citet{InK:04,InK:06} point out, both in-sample and \oos\
methods could be valid, but the \oos\ methods could have lower power.

In this paper, we study the ``overfit'' possibility and leave
``instability'' to future research. This paper uses dimension
asymptotics to study the behavior of \oos\ comparisons when at least
one of the models is overfit---when the number of its regressors
increases with the number of observations so that their ratio remains
positive.  We focus on linear regression models estimated with a fixed
training window, but our basic conclusions should be true for other
estimation strategies and models as well.  Under this asymptotic
theory, the \ols\ coefficient estimator is no longer consistent or
asymptotically normal \citep{Hub:73} and has positive variance in the
limit.  Even so, we show that the usual \oos\ average is
asymptotically normal and can consistently estimate the difference
between the models' expected loss in periods $T+1,T+2,\dots$
conditional on the on the data available in period $T$, a time-series
analogue to the generalization error.\footnote{See, for example,
  \citet{HTF:08}.}  Under these asymptotics, the generalization error
does not converge to the expected performance of the pseudo-true
models, so the in-sample and \oos\ comparisons measure different
quantities and should be expected to give different results for
reasons beyond simple size and power comparisons.  Under our theory,
the model that is closer to the true \dgp\ in population can forecast
worse.  In such a situation, an in-sample comparison would correctly
reject the null hypothesis that the benchmark is true, and an \oos\
comparison would correctly fail to reject the null that the benchmark
is more accurate.\footnote{In a pair of papers similar to ours,
  \citet{ClM:09,ClM:09b} study in-sample and \oos\ tests that the
  larger model has nonzero coefficients that are too close to zero to
  expect the model to forecast more accurately.  Like this paper, they
  argue that the larger model can be true but less accurate.  However,
  they focus on an aspect of the \dgp\ that makes this phenomenon
  likely, while we focus on the coefficient estimates that produce
  less accurate forecasts.}

This result justifies \oos\ comparisons when researchers want to
choose a model for forecasting.  Although there has been little
emphasis on hypothesis testing in this setting, testing is usually
appropriate: there is usually a familiar benchmark model in place, and
the cost of incorrectly abandoning the benchmark for a less accurate
alternative model is higher than the cost of incorrectly failing to
switch to a more accurate alternative.\footnote{These costs can be
  monetary, in the form of computer upgrades, software installation,
  and training, or they can be reputational costs.}
We show that the \dmw\ test lets the forecaster control the
probability of the first error, just as with conventional hypothesis
testing.

Since the models' coefficients are imprecisely estimated in the limit,
the test sample must be small to ensure that the model estimated over
the training sample is similar to the one that will be estimated over
the full sample.  In particular, $P/T \to 0$ is required for
consistent estimation, and $P^2/T \to 0$ is required for valid
confidence intervals and inference.  For larger $P$, the \oos\
comparisons remain asymptotically normal, but are centered on the
forecasting performance associated with the period-$R$ estimates.  In
practice, researchers typically use large values of $P$, so these
studies may be too pessimistic about their models' future accuracy if
they use the \dmw\ test.  Section~\ref{sec:oostheory} lays out the
asymptotic behavior of the \dmw\ test under this limit theory.

Since the \ols\ coefficient estimator is no longer consistent or
asymptotically normal, the F-test and Wald tests are no longer
asymptotically valid.  Moreover, \citet{Efr:86,Efr:04} shows that
naive comparisons of in-sample loss overestimate models' accuracy by a
factor proportional to $K/T$, $K$ being the number of regressors.  But
modifications of the F-test are valid under this asymptotic theory, as
shown by \citet{BoB:95}, \citet{AkA:00}, \citet{AkP:04}, and
\citet{Cal:10b}, among others.  Such results establish that hypotheses
about the parameters of the \dgp\ can be tested in-sample even if one
or both models are overfit.  For that very reason, these tests can not
reliably choose a model for forecasting and will reject the benchmark
too often.  We show this analytically in Section~\ref{sec:insample}.
Moreover, under this asymptotic theory, many recent \oos\ test
statistics, such as those derived by \cite{ClM:01,ClM:05},
\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should behave like the
F-test.  These tests are also designed to reject the benchmark when
the alternative model is true, and so they may reject too often when
the benchmark is false but more accurate.  Obviously, since the
distribution of these statistics converges to the normal when $P/T \to
0$ (with the number of regressors fixed), these statistics behave
like the \dmw\ test when $P$ is small, but should over-reject the
benchmark when $P$ is large.  Section~\ref{sec:mc} presents
simulations that support these claims.

@@

The rest of the paper proceeds as follows.
Section~\ref{sec:assumptions} introduces our notation and assumptions.
Section~\ref{sec:theory} gives the main theoretical results for the
\dmw\ \oos\ test and shows that the F-test rejects the benchmark model
too often when it is false but more accurate than the
alternative. Section~\ref{sec:mc} presents a Monte Carlo study
supporting our theoretical results.  Section~\ref{sec:empirics}
applies the \oos\ statistic to \citepos{GoW:08} dataset
for equity premium prediction, and Section~\ref{sec:conclusion}
concludes.  Proofs and supporting results are listed in the Appendix.

@@

The first assumption is a standard condition on the dependence of the
underlying stochastic array.  We assume that the array is absolutely
regular instead of strong mixing, which is more common in
econometrics, because absolute regularity admits a particular coupling
argument \citep{Ber:79} that is unavailable for strong mixing
sequences.  Please see, for example, \citet{Dav:94} for a discussion
of these mixing conditions.

Assumption \ref{asmp-2} rules out uninteresting cases where the
forecast error vanishes.
\begin{asmp}\label{asmp-2}
  The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
  positive and finite, and all of the eigenvalues of the covariance
  matrix of $x_t$ are uniformly positive and finite as well.  The
  Euclidean norms of the pseudo-true coefficients, $\theta_1$ and
  $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and $|\theta_2|_2 = O(1)$.
  Moreover, there exist a $\delta > 0$ and finite $\Delta$ such that
  \begin{equation*}
    \lVert \lambda_{\max}(X_{iS_{T}}'X_{iS_{T}}) \rVert_{3+\delta}
    \leq S_{T}\, \Delta \\
    \lVert
    \lambda_{\max}(X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})
    \rVert_{3+\delta} \leq S_{T}\, \Delta \\
    \lVert \lambda_{\max}((X_{iS_{T}}'X_{iS_{T}})^{-1}) \rVert_{3+\delta} \leq \Delta/S_{T} \\
    \lVert
    \lambda_{\max}((X_{iS_{T}}'\ep{iS_{T}}\ep{iS_{T}}'X_{iS_{T}})^{-1})\rVert_{3+\delta}
    \leq \Delta/S_{T}
  \end{equation*}
  for all $S_{T} \geq K_{2T}$ and large enough $T$, with $i =
  1,2$,
  \[ X_{iT} \equiv [x_{i1} \quad \dots \quad x_{i,T-\h}]' \]
  and
  \[ \ep{iT} = (\varepsilon_{i,1+\h}, \dots, \varepsilon_{i,T})'.\]
\end{asmp}

@@

This third assumption establishes basic moment and smoothness
conditions for the \oos\ loss.  The differentiability
condition is weak and allows the loss function itself to be
non-differentiable; for example, absolute error and many asymmetric loss functions
satisfy this assumption.

@@

The requirements that $P$ and $R$ grow with $T$ are common.  Parts of
the assumption are new, in particular the requirement that $P^2/T \to
0$.  See Lemma \ref{res-convergence} for a discussion of its
implications.  In practical terms, this assumption requires that the
forecaster plans to use the model for many periods in the future, that
the test sample be large, and that the training sample be much larger,
so that including or excluding the test sample does not affect the
estimates of $\theta_1$ or $\theta_2$ very much.

The next assumption restricts the class of variance estimators we will
consider.  We use the same class of estimators studied by
\citet{DeD:00} (their class $\mathcal{K}$); see
their paper for further discussion.

@@

\begin{thm}\label{res-confidence-intervals}
  Suppose that Assumptions \ref{asmp-1}--\ref{asmp-4} hold, that
  $\hat\sigma$ is an estimator satisfying
  \[
    \hat\sigma^2 = \sigma^2 + o_p(1), \quad \text{with}\quad 
    \sigma^2 \equiv \var_R(\sqrt{P} \bar D_1),
  \]
  and that $\sigma^2$ is uniformly a.s. positive.  Then
  \[
  \frac{\bar{D}_1 - \E_T\bar{D}_2}{\hat\sigma / \sqrt{P}}
  \to^d N(0,1).
  \]
  Consequently, each of the usual Gaussian confidence intervals,
  \begin{eqnarray}
  &&[\bar{D}_1 - z_{\alpha/2} \, \hat\sigma /
      \sqrt{P}, \bar{D}_1 + z_{\alpha/2} \hat\sigma / \sqrt{P}],\label{interval-twosided} \\
  &&[\bar{D}_1 - z_{\alpha} \, \hat\sigma / \sqrt{P}, +\infty), \label{interval-greater}
  \end{eqnarray}
  and
  \begin{equation} (-\infty, \bar{D}_1 + z_{\alpha}
      \, \hat\sigma / \sqrt{P}],
  \end{equation}
  contains $\E_T\bar{D}_2$ with probability $\alpha$ in the limit,
  with $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
  distribution.
\end{thm}
The requirement that $\sigma^2$ be uniformly a.s. positive is not
restrictive under our asymptotic theory.  Since the models'
coefficients are estimated with uncertainty in the limit, the two
models give different forecasts even if they both nest the \dgp.  This
is similar to \citepos{GiW:06} rolling-window result, but comes from
different asymptotics.

@@

Mixingales satisfies a weak-dependence condition similar to \mds es
and were introduced and studied extensively by
\citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.  This lemma shows that the
estimation uncertainty introduces dependence into the \oos\ forecast
errors, but that additional dependence is contained in the term $\E_R
\bar D_1$ and can be effectively removed by subtraction.  The second
part of the Lemma shows that the basic mixingale \clt\ established by
\citet{Dej:97} applies in this setting.\footnote{De Jong proves two
  \clt s: one for mixingales and one for \ned\ functions of mixing
  processes.  His mixingale result makes assumptions about the
  behavior of the sample second moment that arise as consequences of
  \ned.  The proof of Lemma~\ref{res-mixingale} shows that the
  arguments used for de Jong's \ned\ \clt\ continue to hold for our
  \oos\ process---in effect, that the \oos\ process has slightly more
  structure than required for it to be a mixingale.}

@@

Finally, for Theorem \ref{res-confidence-intervals} to be useful, we
need a consistent estimator of $\sigma^2$. Lemma
\ref{res-variance-estimator} establishes that the usual \oos\ \hac\
variance estimators are consistent.\footnote{As with
      Lemma~\ref{res-mixingale}, the proof of this lemma takes
      \citepos{DeD:00} existing consistency results
      for \ned\ processes and shows that the same arguments can be
      applied to our \oos\ mixingale.}

@@

\section{Monte Carlo}\label{sec:mc}
\newcommand{\thetanorm}{\ensuremath{\lvert \theta \rvert_2}} This
section presents two simulations that investigate the accuracy of our
theory in small samples.\footnote{Simulations were conducted in R
  \citep{Rde:10} using the Lattice \citep{Sar:10} and RSQLite
  \citep{Jam:10} packages for graphics and data management
  respectively.}  The first looks at the asymptotic normality of the
\dmw\ statistic centered on either $E_R \bar D_1$ or $E_T \bar D_2$.
The previous section's results imply that centering on the first
should give an approximately normal statistic and centering on the
second should give a normal statistic when $P$ is small relative to
$T$.  The second simulation looks at the size and power of several
statistics when conducting inference about the difference in the
models' generalization error.

@@

Results using \citepos{Mcc:07} critical values are
presented in Figure~\ref{fig:mccracken} and are similar to those using
Clark and West's test.  For $c=0$ the rejection probability is nearly
the test's nominal size.  For $c=1$, the rejection probability
increases with $P/T$, from close to the nominal size when $P/T$ is
small to over 25\% when $P/T = 2/3$.  Note that all of the simulations
use the parsimonious model.  McCracken's statistic over-rejects here
by slightly less than Clark and West's, but still by a substantial
amount.

@@

\appendix
\section{Supporting results}
The results in this paper rely heavily on a coupling argument for
absolutely regular sequences, Berbee's Lemma \citep{Ber:79}.  In fact,
many of the results of this paper (\ref{res-confidence-intervals},
\ref{res-mixingale}, and \ref{res-variance-estimator}) are
modifications of existing results for \ned\ functions of mixing
processes by \citet{Dej:97} and
\citet{DeD:00}; this coupling argument is used to
explicitly derive inequalities that arise naturally for \ned\
processes.  Lemma \ref{lem-basic-coupling} establishes these
inequalities, which are based on a proposition of
\citet{MeP:02}.
